The globular cluster system of the Auriga simulations

### 2020-06-02 AurigaGCS.tex
Smallcase for code and programming languages

\section{Introduction}
Globular star clusters (GC)s are old, bright, and ubiquitous. Various properties of
GC systems (GCS) show correlations with their host galaxies. GCSs are believed to
retain information about the galactic (gas) conditions at their times of formation.
Thus they could offer a unique insight into the (chemodynamical) evolution of their 
parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
is adequately understood. However, despite decades of research (e.g.~\citealt{
1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 2006ARA&A..44..193B, 
2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}), consensus on an 
exhaustive picture of the formation of GCs is yet to be reached. Most galaxies host
a GCS with a bimodal colour distribution that may reflect a bimodal metallicity 
distribution which is argued to arise from two distinct formation channels 
\citep{2006ARA&A..44..193B}. GCs are typically referred to as `blue' or `red' \citep[e.g.][]{
1985ApJ...293..424Z,1999AJ....118.1526G,2001AJ....121.2974L} where the former class
is more metal-poor, more radially extended, and showing little to no rotation wheras
the later is more metal-rich, radially concentrated, and rotating with the galaxy.

The literature offers a wealth of formation scenarios, many of which focus on the
distinct characteristics of the blue or red subpopulation. \citet{1968ApJ...154..891P}
and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
structures in the Universe (i.e. prior to formation of the main galaxy), 
noting that the Jeans length and mass shortly after recombination is consistent
with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
2009ApJ...706L.192B} argue that the blue, metal-poor GCs ([Fe/H]$ < -1$) form in 
radially biased dark matter (DM) halos at high redshift. Other recent hypotheses 
of GC formation prior to collapse of the proto-galaxy include formation in colliding 
supershells \citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
\citep{2019arXiv190408941C}, or in high-speed collisions of dark matter subhaloes
\citep{2019arXiv190508951M}. \citet{2017MNRAS.472.3120B} suggests
that (the blue subpopulation of) GCs could form in high density regions along
the cosmic filament before or during collapse.

@@

Yet another hypothesis is that star cluster formation is triggered by major 
gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
which is naturally expected within the framework of hierarchical assembly. One
testable prediction of this scenario is the formation of young clusters in
interacting and merging galaxies, which has been observed and are found to show 
remarkable similarities with GCs in the Milky Way (MW) \citep[e.g.][]{
1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
produces star clusters that could be GC progenitors \citep{
2019arXiv190509840L}.

As for the formation timeline, the scenarios (and flavours thereof) of \citet{
1985ApJ...298...18F} and \citet{1992ApJ...384...50A} are intertwined because
accretion and mergers continuously occurs during the hierarchical build-up of
galaxies. Various (other) hierarchical formation channels thus combine different
aspects of the aforementioned paradigms, such as GC formation in (small) galactic
disks before they are accreted onto an assembling galaxy \citep[e.g.][]{
2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B, 2003egcs.conf..224G}. 
We refer to \citet{2001astro.ph..8034G} for a scoreboard of GC formation models 
compared to observations of the MW GCSs.

An idea that has recently been studied extensively is the hypothesis that the formation
mechanisms of young massive clusters \citep[YMCs, see][for a review]{2010ARA&A..48..431P} 
and GCs are the same. The proximity of YMCs in the local Universe allows to study these 
processes with a level of detail that cannot be achieved for GCs at high redshifts. In 
this framework, differences between both classes of objects are caused by nearly a 
Hubble time of (dynamical) evolution \citep[e.g.][]{1987degc.book.....S}. This picture 
is based on observed similarities between YMCs and GCs
\citep[e.g.][]{1992AJ....103..691H,1999AJ....118.1551W} and strengthened by observations
of gravitationally lensed objects at high redshifts ($z = 2-6)$. These sources have 
properties reminiscent of (local) YMCs and may be GC progenitors at times of formation 
\citep{2017MNRAS.467.4304V,2017ApJ...843L..21J}. The modelling work by 
\citet{2011MNRAS.414.1339K,2012MNRAS.421.1927K,2015MNRAS.454.1658K} is now 
incorporated into cosmological zoom simulations and shows promising results
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.

The (mass) resolution of cosmological zoom simulations has reached the mass range 
populated by GCs, and the gravitational force softening can be as low several 
parsec. A number of groups can thus incorporate formation of (globular) star 
clusters into their high-resolution hydrodynamical simulations. \citet{2016ApJ...831..204R} 
ran parsec scale simulations of the high-redshift universe 
prior to reionization (the simulations stop at $z=9$), \citet{2017ApJ...834...69L} 
implement a new subgrid model for star (cluster) formation and run simulations 
that reach $z=3.3$, and the run of \citet{2017MNRAS.465.3622R} reaches $z=0.5$. 
\citet{2018MNRAS.474.4232K} find that mergers can push gas to high density that
quickly forms clustered stars that end up tightly bound by the end of the 
simulation. A somewhat different approach couples semi-analytical models to DM-only
simulations \citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
2019MNRAS.486..331C,2019arXiv190505199C}, as is done in the work by 
\citet{2019MNRAS.482.4528E}.

In this work we use state of the art simulations that produce realistic spiral 
galaxies (MW analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GCS similar to 
the MW and/or Andromeda (M31) GCSs. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Section~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, radial, and metallicity-radial 
distributions that are consistent with the MW and/or M31 GCSs, and whether the 
model produces enough stellar mass with the right properties. Moreover, the simulations
provide us with the history of the star particles, which allows us to investigate
the differences between these properties for sub populations that have formed 
{\it in~situ} versus those that have been accreted. We focus on the metallicity
and radial distributions because observations of the red and blue GCs show
distinct differences between these properties.

The plan of the paper is as follows. We summarise the relevant characteristics 
of the Auriga simulations in section~\ref{sec:auriga}, followed by a summary of 
the observations of the MW and M31 GCSs
in section~\ref{sec:observations} that we use to compare our simulations to in
section~\ref{sec:results}. We discuss our findings in section~\ref{sec:discussion}
to come to our conclusions in section~\ref{sec:conclusions}.

% Referee: ``\citet{2012MNRAS.426.1475U} shows the great variety in GC metallicity distributions
% present in the sample of early-type galaxies of the SLUGGS survey contradicts
% the classical idea that all the metallicity distributions of GCs should be bimodal.''

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citepalias{2017MNRAS.467..179G}, a suite of 
high-resolution cosmological zoom simulations of MW analogues. The MW-mass
selected initial conditions in the range $1-2 \times 10^{12}$~M$_{\odot}$
were selected from the \mbox{\textsc{eagle}} DM only box, see 
\citetalias{2017MNRAS.467..179G} for details. The simulations are 
performed with the \textsc{arepo} code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} 
that solves the magnetohydrodynamical equations on a moving mesh.

The galaxy formation model includes primordial and metal-line cooling with 
self-shielding corrections. Reionization is completed at redshift $6$ by a
time-varying spatially uniform UV background \citep{2009ApJ...703.1416F, 
2013MNRAS.436.3031V}. The interstellar medium (ISM) is described by an equation of 
state for a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}: 
cold clouds embedded in a hot ambient medium, whose mass and energy densities
are described by processes important for star formation, such as the condensation 
of cold clouds and the photoevaporation of clouds. Stars form stocastically in 
thermally unstable gas with a density threshold of $n = 0.13 \, \text{cm}^{-3}$,
and consecutive stellar evolution is accounted for. The channel for energetic
stellar feedback is from non-local type II supernovae (SN), which is modelled 
with wind particles (\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}).
Galactic winds enrich the ISM with metals from SNIa, SNII, and asymptotic giant 
branch (AGB) stars \citep{2013MNRAS.436.3031V}. Supermassive
black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,
1952MNRAS.112..195B}, and feedback from the active galactic nuclei has a low-accretion
and high-accretion mode (radio and quasar) (\citealt{2005MNRAS.361..776S, 
2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Finally, the simulations 
follow the evolution of a magnetic field of $10^{-14}$ (comoving)~G seeded at 
$z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.

@@

\subsection{Andromeda}
\label{sec:andromeda}
\citet[][hereafter C11]{2011AJ....141...61C} and \citet[][hereafter CR16]{2016ApJ...824...42C}
present a uniform set of spectroscopic observations of the inner 
$1.6^\circ~({\sim}21)$~kpc of M31 that is believed to be 94\% complete. In addition,
the outer stellar halo of M31 up to $r_{\text{proj}}\sim150$~kpc is observed in 
the Pan-Andromeda Archaeological Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H,
2014MNRAS.442.2929V, 2019MNRAS.484.1756M}. In fact, 
the work of H14 is incorporated in the latest public release\footnote{Last 
revised 23 Sep 2015, see \url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 and CR16 data sets. Therefore we use the latest data set of CR16 
because it is the most recent aggregated dataset of M31's GCS that contains GCs 
in the inner region and in the outer halo. The relevant fields in the CR16 dataset 
that we use are the age, metallicity, and the mass-estimate\footnote{The authors 
assumed $M/L_V = 2$ independent of [Fe/H]}. We calculate the galactocentric radii 
from the observed positions RA and DEC, further discussed in Sec.~\ref{sec:Rgc}.

\subsection{Age-estimates}
\label{sec:age}
The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
in CR16. The mean age of the MW GCs in this data set is $11.9$~Gyr and the 
standard deviation is $0.8$~Gyr. Furthermore, only 1 of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0$~Gyr with a standard deviation 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCSs are not statistically consistent. Moreover, the MW appears 
to host a GCS that is somewhat older than that of M31.
This is somewhat surprising given that M31 is generally considered to be earlier
type than the MW meaning that an older stellar population would be naively expected.
However, we do caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

\subsection{Radial distribution}
\label{sec:Rgc}
The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
of the MW and M31 GCS. We divide the radii of M31 by its virial radius\footnote{
$r_{\text{vir}}$ is the radius in a spherical `top-hat' perturbation model at which
the average density reaches an overdensity of $\Delta_{\text{vir}}=357$ times the 
background density} $r_{\text{vir,M31}} = 299$~kpc and multiply by 
$r_{\text{vir,MW}} = 261$~kpc to account for the different intrinsic sizes of both 
galaxies, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}.
Values for $r_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), 
but the galactocentric radius of GCs in M31 is not available in CR16. Therefore, we 
follow \citet[][section~4.1]{2019arXiv190111229W} 
to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
adopting M31's central position from the NASA Extragalactic 
Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
We calculate $r_{\text{gal}}$ as `average deprojected distance`
$r_{\text{gal}} = r_{\text{proj}} \times (4/\pi)$.

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that few age-estimates are available 
for the innermost ($<1$~kpc) GCs, and none for those beyond roughly $20$~kpc
(the halo GCs). We compare both distributions of the full data set (solid 
lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
when accounting for the larger number of total GCs in M31. Interestingly, both
distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
subpopulation of halo GCs. Our naive expectation would be that the spiral galaxies
in the Local Group host similar GC systems. However, the radial distributions of
the GCS of the MW and M31 are not statistically consistent with being drawn from 
the same underlying distribution due to substantial differences at intermediate radii.

@@

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older
than $10$~Gyr based on the age distribution of the MW GCS (top panel of 
Figure~\ref{fig:MW-M31-age-Rgc}), adopting the definition of a GC from
\citet{2010ARA&A..48..431P} and following the method of 
\citet{2017MNRAS.465.3622R}. However, we caution that his definition does exclude 
1 GC in the MW and 24 in M31 as stated in Section~\ref{sec:age}, and further
discuss this in Section~\ref{sec:age_min}.

Throughout our analysis we compare distributions of age-selected GC 
candidates (age $>10$~Gyr) with those of all star particles (i.e.
when no additional selection criterion is applied). The mean number of star 
particles in the Auriga L4 simulations that we select as GC candidates is 
$3.1 \cdot 10^5$ (with a mean total mass of $1.15 \cdot 10^{10}$ M$_{\odot}$), 
and the mean number of all star particles is $1.93 \cdot 10^6$ 
($7.3\cdot10^{10}$ M$_{\odot}$). The subset of GC candidates is thus around 
15\% of all the stars in the galaxy when averaged over all Auriga L4 haloes. 
We further split the GC
candidates into an {\it in~situ} subset (defined as GC candidates that are 
bound to the most-massive halo/subhalo in the first snapshot that the particle 
was recorded), and an accreted subpopulation (those that have formed {\it ex~situ} and 
are bound to the most-massive halo/subhalo at $z=0$). A GC candidate either formed
{\it in~situ} or it was accreted. We consider the metallicity distribution in 
Sec.~\ref{sec:results_FeH}, the distribution of galactocentric radii in 
Sec.~\ref{sec:results_Rgc}, and the combination of both 
in Sec.~\ref{sec:results_FeHRgc}.

@@

To ease this comparison between the simulations and observations we take the ratio
of the total mass of GC candidates in Auriga to the total GC mass in the observations.
We use a diverging colour map centered around the overall median of the 
mass ratio (i.e. we subtract the median of these $25$ bins from the value 
in each bin). We show this in the top and bottom panel of Figure~\ref{fig:Au-FeHRgc-ratio}
for the MW and M31, respectively. Note that the 3 bins in the top right are empty (white)
because the mass ratio cannot be calculated due to zero mass in the observations.
If the product of the bound cluster formation efficiency and consecutive GC 
disruption over a Hubble time would be constant, then the value in each bin would
be zero. The red and blue bins indicate deviations from such a scenario and
indicate a higher and lower than average mass excess in the simulations. The median 
value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
respectively. This means that the median `mass budget' that the simulations `can 
afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
The lowest mass surplus for both galaxies is the bin with metallicities in the range
[Fe/H]~$\in [-2.5, -1.5]$ and gallactocentric radius $r_{\text{gal}}\in [3,8]$~kpc,
for which the simulations produce 
a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
more mass in GC candidates than what is observed in the MW and M31 respectively.
The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
for M31.

>>>>

\section{Introduction}
Globular star clusters (GC)s are old, bright, and ubiquitous. Various properties of
GC systems (GCS) show correlations with their host galaxies. GCSs are believed to
retain information about the galactic (gas) conditions at their times of formation.
Thus they could offer a unique insight into the (chemodynamical) evolution of their 
parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
is adequately understood. However, despite decades of research (e.g.~\citealt{
1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 2006ARA&A..44..193B, 
2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}), consensus on an 
exhaustive picture of the formation of GCs is yet to be reached. Most galaxies host
a GCS with a bimodal colour distribution that may reflect a bimodal metallicity 
distribution which is argued to arise from two distinct formation channels 
\citep{2006ARA&A..44..193B}. GCs are typically referred to as `blue' or `red' \citep[e.g.][]{
1985ApJ...293..424Z,1999AJ....118.1526G,2001AJ....121.2974L} where the former class
is more metal-poor, more radially extended, and showing little to no rotation whereas
the latter is more metal-rich, radially concentrated, and rotating with the galaxy.

The literature offers a wealth of formation scenarios, many of which focus on the
distinct characteristics of the blue or red subpopulation. \citet{1968ApJ...154..891P}
and \citet{1984ApJ...277..470P} argue that GCs form as the earliest bound
structures in the Universe (i.e. prior to formation of the main galaxy), 
noting that the Jeans length and mass shortly after recombination is consistent
with typical GC masses and sizes. \citet{2005MNRAS.364..367D} and \citet{
2009ApJ...706L.192B} argue that the blue, metal-poor GCs ([Fe/H]$ < -1$) form in 
radially biased dark matter (DM) halos at high redshift. Other recent hypotheses 
of GC formation prior to collapse of the proto-galaxy include formation in colliding 
supershells \citep{2017Ap&SS.362..183R}, in supersonically induced gaseous objects
\citep{2019ApJ...878L..23C}, or in high-speed collisions of dark matter subhaloes
\citep{2020ApJ...890...18M}. \citet{2017MNRAS.472.3120B} suggests
that (the blue subpopulation of) GCs could form in high density regions along
the cosmic filament before or during collapse.

@@

Yet another hypothesis is that star cluster formation traces periods of high-intensity
star formation, which can be triggered by major gas-rich (spiral) galaxy mergers 
\citep{1987nngp.proc...18S, 1992ApJ...384...50A}. Such a scenario is naturally 
expected within the framework of hierarchical assembly and predicts formation 
of young clusters in interacting and merging galaxies, which has been observed 
and are found to show remarkable similarities with GCs in the Milky Way (MW) \citep[e.g.][]{
1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
produces star clusters that could be GC progenitors \citep{2019ApJ...879L..18L}.

As for the formation timeline, the scenarios (and flavours thereof) of \citet{
1985ApJ...298...18F} and \citet{1992ApJ...384...50A} are intertwined because
accretion and mergers continually occur during the hierarchical build-up of
galaxies. Various (other) hierarchical formation channels thus combine different
aspects of the aforementioned paradigms, such as GC formation in (small) galactic
disks before they are accreted onto an assembling galaxy \citep[e.g.][]{
2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B, 2003egcs.conf..224G}. 
We refer to \citet{2001astro.ph..8034G} for a scoreboard of GC formation models 
compared to observations of the MW GCSs.

An idea that has recently been studied extensively is the hypothesis that the formation
mechanisms of young massive clusters \citep[YMCs, see][for a review]{2010ARA&A..48..431P} 
and GCs are the same. The proximity of YMCs in the local Universe allows to study these 
processes with a level of detail that cannot be achieved for GCs at high redshifts. In 
this framework, differences between the two classes of objects are caused by nearly a 
Hubble time of (dynamical) evolution \citep[e.g.][]{1987degc.book.....S}. This picture 
is based on observed similarities between YMCs and GCs
\citep[e.g.][]{1992AJ....103..691H,1999AJ....118.1551W} and strengthened by observations
of gravitationally lensed objects at high redshifts ($z = 2-6)$. These sources have 
properties reminiscent of (local) YMCs and may be GC progenitors at times of formation 
\citep{2017MNRAS.467.4304V,2017ApJ...843L..21J}. The modelling work by 
\citet{2011MNRAS.414.1339K,2012MNRAS.421.1927K,2015MNRAS.454.1658K} is now 
incorporated into cosmological zoom simulations and shows promising results
\citep{2018MNRAS.475.4309P,2019MNRAS.486.3134K}.

The (mass) resolution of cosmological zoom simulations has reached the mass range 
populated by GCs, and the gravitational force softening can be as low as several 
parsec. A number of groups can thus incorporate formation of (globular) star 
clusters into their high-resolution hydrodynamical simulations. \citet{2016ApJ...831..204R} 
ran parsec scale simulations of the high-redshift universe 
prior to reionization (the simulations stop at $z=9$), \citet{2017ApJ...834...69L} 
implement a new subgrid model for star (cluster) formation and run simulations 
that reach $z=3.3$, and the run of \citet{2017MNRAS.465.3622R} reaches $z=0.5$. 
\citet{2018MNRAS.474.4232K} find that mergers can push gas to high density that
quickly forms clustered stars that end up tightly bound by the end of the 
simulation. A somewhat different approach couples semi-analytical models to DM-only
simulations \citep{2010ApJ...718.1266M,2014ApJ...796...10L,2018MNRAS.480.2343C,
2019MNRAS.486..331C,2019MNRAS.488.5409C}, also done in the work by 
\citet{2019MNRAS.482.4528E}.

In this work we use state of the art simulations that produce realistic spiral 
galaxies (MW analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations could give rise to a GCS similar to 
the MW and/or Andromeda (M31) GCSs. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Section~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, radial, and metallicity-radial 
distributions that are consistent with the MW and/or M31 GCSs, and whether the 
model produces enough stellar mass with the right properties. Moreover, the simulations
provide us with the history of the star particles, which allows us to investigate
the differences between these properties for sub-populations that have formed 
{\it in~situ} versus those that have been accreted. We focus on the metallicity
and radial distributions because observations of the red and blue GCs show
distinct differences between these properties.

The plan of the paper is as follows. We summarise the relevant characteristics 
of the Auriga simulations in Section~\ref{sec:auriga}, followed by a summary of 
the observations of the MW and M31 GCSs
in Section~\ref{sec:observations} that we compare our simulations to in
Section~\ref{sec:results}. We discuss our findings in Section~\ref{sec:discussion}
to come to our conclusions in Section~\ref{sec:conclusions}.

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citepalias{2017MNRAS.467..179G}, a suite of 
high-resolution cosmological zoom simulations of MW analogues. The MW-mass
selected initial conditions in the range $1-2 \times 10^{12}$~M$_{\odot}$
were selected from the \mbox{\textsc{eagle}} DM-only box, see 
\citetalias{2017MNRAS.467..179G} for details. The simulations are 
performed with the \textsc{arepo} code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} 
that solves the magnetohydrodynamical equations on a moving mesh.

The galaxy formation model includes primordial and metal-line cooling with 
self-shielding corrections. Reionization is completed at redshift $6$ by a
time-varying spatially uniform UV background \citep{2009ApJ...703.1416F, 
2013MNRAS.436.3031V}. The interstellar medium (ISM) is described by an equation of 
state for a two-phase medium in pressure equilibrium \citep{2003MNRAS.339..289S}: 
cold clouds embedded in a hot ambient medium, whose mass and energy densities
are described by processes important for star formation, such as the condensation 
of cold clouds and the photoevaporation of clouds. Stars form stochastically in 
thermally unstable gas with a density threshold of $n = 0.13 \, \text{cm}^{-3}$,
and consecutive stellar evolution is accounted for. The channel for energetic
stellar feedback is from non-local type II supernovae (SN), which is modelled 
with wind particles (\citealt{2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}).
Galactic winds enrich the ISM with metals from SNIa, SNII, and asymptotic giant 
branch stars \citep{2013MNRAS.436.3031V}. Supermassive
black holes grow via Bondi–Hoyle–Lyttleton accretion \citep{1944MNRAS.104..273B,
1952MNRAS.112..195B}, and feedback from the active galactic nuclei has a low-accretion
and high-accretion mode (radio and quasar) (\citealt{2005MNRAS.361..776S, 
2014MNRAS.437.1750M}; \citetalias{2017MNRAS.467..179G}). Finally, the simulations 
follow the evolution of a magnetic field of $10^{-14}$ (comoving)~G seeded at 
$z = 127$ \citep{2013MNRAS.432..176P, 2014ApJ...783L..20P}.

@@

\subsection{Andromeda}
\label{sec:andromeda}
\citet[][hereafter C11]{2011AJ....141...61C} and \citet[][hereafter CR16]{2016ApJ...824...42C}
present a uniform set of spectroscopic observations of the inner 
$1.6^\circ~({\sim}21)$~kpc of M31 that is believed to be 94\% complete. In addition,
the outer stellar halo of M31 up to $r_{\text{proj}}\sim150$~kpc is observed in 
the Pan-Andromeda Archaeological Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H,
2014MNRAS.442.2929V, 2019MNRAS.484.1756M}. In fact, 
the work of H14 is incorporated in the latest public release\footnote{Last 
revised 23 Sep 2015, see \url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 and CR16 data sets. Therefore we use the latest data set of CR16 
because it is the most recent aggregated dataset of M31's GCS that contains GCs 
in the inner region and in the outer halo. The relevant fields in the CR16 dataset 
that we use are the age, metallicity, and the mass-estimate\footnote{The authors 
assumed $M/L_V = 2$ independent of [Fe/H]}. We calculate the galactocentric radii 
from the observed positions RA and DEC, as further discussed in Section~\ref{sec:Rgc}.

\subsection{Age-estimates}
\label{sec:age}
The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
in CR16. The mean age of the MW GCs in this data set is $11.9$~Gyr and the 
standard deviation is $0.8$~Gyr. Furthermore, only 1 of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0$~Gyr with a standard deviation 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCSs are not statistically consistent. The MW appears 
to host a GCS that is somewhat older than that of M31.
This is somewhat surprising given that M31 is generally considered to be earlier
type than the MW so that an older stellar population would naively be expected.
On the other hand, the MW could be an outlier as it may have formed and assembled 
most of its mass earlier than galaxies with a similar mass \citep[e.g.][]{2014ApJ...781L..31S,
2015A&A...578A..87S,2018MNRAS.477.5072M}.
In addition, we caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

\subsection{Radial distribution}
\label{sec:Rgc}
The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
of the MW and M31 GCS. We divide the radii of M31 by its virial radius\footnote{
$r_{\text{vir}}$ is the radius in a spherical `top-hat' perturbation model at which
the average density reaches an overdensity of $\Delta_{\text{vir}}=357$ times the 
background density} $r_{\text{vir,M31}} = 299$~kpc and multiply by 
$r_{\text{vir,MW}} = 261$~kpc to account for the different intrinsic sizes of the two
galaxies, adopting the values and cosmology from \citet{2017MNRAS.464.3825P}.
Values for $r_{\text{gal}}$ are readily available in H96e10 (assuming $r_{\odot}=8.0$~kpc), 
but the galactocentric radius of GCs in M31 is not available in CR16. Therefore, we 
follow \citet[][section~4.1]{2019A&A...623A..65W} 
to calculate the projected radius $r_{\text{proj}}$ from the observed positions,
adopting M31's central position from the NASA Extragalactic 
Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and the distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
We estimate $r_{\text{gal}}$ as `average deprojected distance`
$r_{\text{gal}} = r_{\text{proj}} \times (4/\pi)$.

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that few age-estimates are available 
for the innermost ($<1$~kpc) GCs, and none for those beyond roughly $20$~kpc
(the halo GCs). We compare the two distributions of the full data set (solid 
lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
when accounting for the larger number of total GCs in M31. Interestingly, the two 
distributions show a similar trend for $r_{\text{gal}} > 4$~kpc and host a 
subpopulation of halo GCs. Our naive expectation would be that the spiral galaxies
in the Local Group host similar GC systems. However, based on a two-sample KS test
we find that the radial distributions of the GCS of the MW and M31 are not statistically 
consistent with being drawn from the same underlying distribution due to substantial 
differences at intermediate radii.

@@

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older
than $10$~Gyr based on the age distribution of the MW GCS (top panel of 
Figure~\ref{fig:MW-M31-age-Rgc}), adopting the definition of a GC from
\citet{2010ARA&A..48..431P} and following the method of 
\citet{2017MNRAS.465.3622R}. However, we caution that this definition, although 
statistically consistent with the estimated ages of all GCs in the MW, is not 
consistent with the tail of younger clusters as stated in Section~\ref{sec:age},
and further discussed in Section~\ref{sec:age_min}.

Throughout our analysis we compare distributions of age-selected GC 
candidates (age $>10$~Gyr) with those of all star particles (i.e.
with no age cut). The mean number of star 
particles in the Auriga L4 simulations that we select as GC candidates is 
$3.1 \cdot 10^5$ (with a mean total mass of $1.15 \cdot 10^{10}$ M$_{\odot}$), 
and the mean number of all star particles is $1.93 \cdot 10^6$ 
($7.3\cdot10^{10}$ M$_{\odot}$). The subset of GC candidates is thus around 
15\% of all the stars in the galaxy when averaged over all Auriga L4 haloes. 
We further split the GC
candidates into an {\it in~situ} subset (defined as GC candidates that are 
bound to the most-massive halo/subhalo in the first snapshot that the particle 
was recorded), and an accreted subpopulation (those that have formed {\it ex~situ} but
are bound to the most-massive halo/subhalo at $z=0$). A GC candidate either formed
{\it in~situ} or it was accreted. We consider the metallicity distribution in 
Section~\ref{sec:results_FeH}, the distribution of galactocentric radii in 
Section~\ref{sec:results_Rgc}, and the combination of the two 
in Section~\ref{sec:results_FeHRgc}.

@@

To ease this comparison between the simulations and observations we take the ratio
of the total mass of GC candidates in Auriga to the total GC mass in the observations.
We use a diverging colour map centered around the overall median of the 
mass ratio (i.e. we subtract the median of these $25$ bins from the value 
in each bin). We show this in the top and bottom panel of Figure~\ref{fig:Au-FeHRgc-ratio}
for the MW and M31, respectively. Note that the 3 bins in the top right are empty (white)
because the mass ratio cannot be calculated due to zero mass in the observations.
If the product of the bound cluster formation efficiency and consecutive GC 
disruption over a Hubble time would be constant, then the value in each bin would
be zero. The red and blue bins indicate deviations from such a scenario and
indicate a higher and lower than average mass excess in the simulations. The median 
value used to shift the mass ratio is $2.68$ and $1.69$ dex for the MW and M31, 
respectively. This means that the median `mass budget' that the simulations `can 
afford to lose' is roughly a factor $480$ and $50$ for the MW and M31, respectively. 
The lowest mass surplus for both galaxies is the bin with metallicities in the range
[Fe/H]~$\in [-2.5, -1.5]$ and galactocentric radius $r_{\text{gal}}\in [3,8]$~kpc,
for which the simulations produce 
a factor $10^{2.68}/10^{1.33} \approx 22$ and $10^{1.69}/10^{0.75} \approx 9$ 
more mass in GC candidates than is observed in the MW and M31 respectively.
The highest factor for the MW is $2.1 \times 10^{5}$, and $1.1 \times 10^{3}$
for M31.
